...

### 2024-12-03 paper/paper.qmd
working on creating a figure for results section

>>>>

```{r}
#| echo: false 
#| message: false
#| label: fig-familysizedistribution
#| fig-cap: Number of 2, 3, and 4-person Census Families Across Toronto Neighbourhoods

family_size <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
#view(family_size)

family_size$`Neighbourhood Number` = as.numeric(as.character(family_size$`Neighbourhood Number`))
family_size$`2 persons` = as.numeric(as.character(family_size$`2 persons`))
family_size$`3 persons` = as.numeric(as.character(family_size$`3 persons`))
family_size$`4 persons` = as.numeric(as.character(family_size$`4 persons`))

ggplot(family_size, aes(x = "Neighbourhood Name", y = "2 persons")) + 
  geom_line(linewidth = 0.5, colour="black") + geom_point(colour = "black") +
 theme_light()  
  ggtitle("EMS Demand From 2017 to 2022") +
  labs(x = "Year", y = "Demand for EMS", caption = "Data Source: Toronto Paramedic Services") + 
  theme(plot.title = element_text(hjust = 0.5)) 
```
